---
title: "Industrial Survey"
author: "Arturo Torre"
date: "23/10/2018"
output: html_document
---
## Mexican Industrial Survey {.tabset .tabset-fade .tabset-pills}

###Intro

```{r, include=FALSE}
library(dplyr)
library(ggplot2)
library(magrittr)
library(tidyr)
library(knitr)
library(reshape)
library(viridis)
library(gridExtra)
library (scales)
```

```{r}
#We load the data imported directly from INEGI´s website. 
datos <- read.csv(file="datos.csv", header=TRUE, sep=",")
```
It is important to mention that we have aggregated variables by sector and subsector. 


```{r, include=FALSE}
#We will also load the dictionary from INEGI´s website to know the meaning of column names.
diccionario <- read.csv(file="diccionario.csv", header=TRUE, sep=",")

head(diccionario)
```

As we can see we have worked hours, number of employees, supplies imported among many other variables.

Notice that data provided by INEGI presents different levels of aggregation. Following NAICS system we have information a 2,4 and/or 6 figure code. This survey also includes a general category named 31-33 which aggregates all the available information. We will start with a general overview of the Mexican Industry followed by particular industry analysis. 

We will follow Hadley Wickham´s tidy data format mainly by subsetting particular data from the survey´s raw data.


###General Industrial Manufacturing
```{r}
manuf <- datos %>% select(CODIGO_SCIAN, ANIO, H010B, H010C) %>% filter(CODIGO_SCIAN %in% c("31-33"))
```
In this section we will analyse the general overview of industrial manufacturing in Mexico. 

```{r}
#For easy handing we must use the tidy data paradigm
manuf_tidy <- manuf %>% gather(Genero,Numero,H010B:H010C) 
manuf_tidy$Genero[manuf_tidy$Genero == "H010B"] <- "Hombres"
manuf_tidy$Genero[manuf_tidy$Genero == "H010C"] <- "Mujeres"
```


```{r,include=FALSE}
manuf1 <-  ggplot(data = manuf_tidy, aes(x=ANIO, y=Numero, color=Genero)) + 
  geom_line(size=5) +
  xlab('Año') +
  ylab('Número de Empleados') +
  ggtitle("Empleados divididos por género en la industria manufacturera") +
  theme(plot.title = element_text(hjust = 0.5))  +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_y_continuous(labels = comma)
  
```

```{r}
manuf1 
```

```{r}
manuf_ins <- datos %>% select(CODIGO_SCIAN, ANIO, K316B, K316C) %>% filter(CODIGO_SCIAN %in% c("31-33"))
```

```{r}
#For easy handing we must use the tidy data paradigm
manuf_tidy <- manuf_ins %>% gather(Origen, Cantidad, K316B:K316C) 
manuf_tidy$Origen[manuf_tidy$Origen == "K316B"] <- "Nacional"
manuf_tidy$Origen[manuf_tidy$Origen == "K316C"] <- "Importado"
```

```{r,include=FALSE}
manuf2 <-  ggplot(data = manuf_tidy, aes(x=ANIO, y=Cantidad, color=Origen)) + 
  geom_line(size=5) +
  xlab('Año') +
  ylab('Compra de materias primas') +
  ggtitle("Volumen de Materias Primas en la industria manufacturera") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_y_continuous(labels = comma)
  
```

```{r}
manuf2 
```

```{r}
manuf_vtas <- datos %>% select(CODIGO_SCIAN, ANIO, M310B, M310C) %>% filter(CODIGO_SCIAN %in% c("31-33"))
```

```{r}
#For easy handing we must use the tidy data paradigm
manuf_tidy <- manuf_vtas %>% gather(Destino, Ventas, M310B:M310C) 
manuf_tidy$Destino[manuf_tidy$Destino == "M310B"] <- "Nacional"
manuf_tidy$Destino[manuf_tidy$Destino == "M310C"] <- "Exportación"
```

```{r,include=FALSE}
manuf3 <-  ggplot(data = manuf_tidy, aes(x=ANIO, y=Ventas, color=Destino)) + 
  geom_line(size=5) +
  xlab('Año') +
  ylab('Venta de productos finales') +
  ggtitle("Destino de productos finales en la industria manufacturera") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_y_continuous(labels = comma)
  
```

```{r}
manuf3 
```
At 6 figure level we 240 different industries.
```{r, include=FALSE}
inf <-c("311110",	"311211", "311212", "311213", "311215",	"311221",	"311222",	"311230",	"311311",	"311320",	"311330",	"311340",	"311411",	"311422",	"311423",	"311511",	"311512",	"311513",	"311611",	"311612",	"311613",	"311710",	"311811",	"311812",	"311820",	"311830",	"311910",	"311921",	"311922",	"311923",	"311930",	"311940",	"311991",	"311992",	"311999",	"312111",	"312112",	"312120",	"312131",	"312141",	"312142",	"312149",	"312210",	"312221",	"313112",	"313113",	"313210",	"313220",	"313230",	"313240",	"313310",	"313320",	"314110",	"314120",	"314911",	"314912",	"314992",	"314993",	"314999",	"315110",	"315191",	"315192",	"315221",	"315222",	"315223",	"315229",	"315991",	"315999",	"316110",	"316211",	"316212",	"316213",	"316991",	"316999",	"321111",	"321112",	"321113",	"321210",	"321910",	"321920",	"321993",	"322122",	"322132",	"322210",	"322220",	"322230",	"322291",	"322299",	"323111",	"323119",	"324110",	"324120",	"324191",	"325110",	"325120",	"325130",	"325180",	"325190",	"325211",	"325212",	"325220",	"325310",	"325320",	"325411",	"325412",	"325510",	"325520",	"325610",	"325620",	"325910",	"325991",	"325992",	"325999",	"326110",	"326120",	"326130",	"326140",	"326150",	"326160",	"326191",	"326192",	"326193",	"326194",	"326198",	"326199",	"326211",	"326220",	"326290",	"327112",	"327121",	"327122",	"327123",	"327211",	"327213",	"327214",	"327215",	"327219",	"327310",	"327320",	"327330", "327391",	"327410",	"327420",	"327910",	"327991",	"327999",	"331111",	"331112",	"331210",	"331220",	"331310",	"331411",	"331412",	"331419",	"331420",	"331510",	"331520",	"332110",	"332211",	"332212",	"332310",	"332320",	"332410",	"332420",	"332430",	"332510",	"332610",	"332720",	"332810",	"332910",	"332991",	"332999",	"333111",	"333112",	"333120",	"333130",	"333220",	"333291",	"333292",	"333299",	"333319",	"333411",	"333412",	"333510",	"333610",	"333910",	"333920",	"333991",	"333992",	"333999",	"334110",	"334210",	"334220",	"334290",	"334310",	"334410",	"334519",	"334610",	"335110",	"335120",	"335210",	"335220",	"335311",	"335312",	"335910",	"335920",	"335930",	"335991",	"335999",	"336110",	"336120",	"336210",	"336310",	"336320",	"336330",	"336340",	"336350",	"336360",	"336370",	"336390",	"336410",	"336510",	"336610",	"336991", "336992",	"337120",	"337210",	"337910",	"337920",	"339111",	"339112",	"339113",	"339912",	"339920",	"339930",	"339940",	"339992",	"339993",	"339994",	"339999")
```

```{r, include=FALSE}
manuf_6 <- datos %>% select(CODIGO_SCIAN, ANIO, M310B, M310C) %>% filter(CODIGO_SCIAN %in% c(inf))
```

```{r, include=FALSE}
#To see if all the 6-digit categories match in both groups
inf[!(inf %in% manuf_6$CODIGO_SCIAN)]
```




```{r, include=FALSE}
#For easy handing we must use the tidy data paradigm

manuf_tidy_6vtas <- manuf_6 %>% gather(Destino, Ventas, M310B:M310C) 
manuf_tidy_6vtas$Destino[manuf_tidy_6vtas$Destino == "M310B"] <- "Nacional"
manuf_tidy_6vtas$Destino[manuf_tidy_6vtas$Destino == "M310C"] <- "Exportación"
#We filter for 2016 values
manuf_tidy_6vtas <- manuf_tidy_6vtas %>% filter (ANIO==2016)
#We add a column named group
manuf_tidy_6vtas$group <- substr(manuf_tidy_6vtas$CODIGO_SCIAN, 0, 3)
manuf_tidy_6vtas$group <- as.factor(manuf_tidy_6vtas$group)
manuf_tidy_6vtas <- manuf_tidy_6vtas %>% select(CODIGO_SCIAN, Destino, Ventas, group)
```

```{r, include=FALSE}
# Set a number of 'empty bar' to add at the end of each group
empty_bar=2
nObsType=nlevels(as.factor(manuf_tidy_6vtas$Destino))
to_add = data.frame( matrix(NA, empty_bar*nlevels(manuf_tidy_6vtas$group)*nObsType, ncol(manuf_tidy_6vtas)) )
colnames(to_add) = colnames(manuf_tidy_6vtas)
to_add$group=rep(levels(manuf_tidy_6vtas$group), each=empty_bar*nObsType )
data=rbind(manuf_tidy_6vtas, to_add)
data=data %>% arrange(group, CODIGO_SCIAN)
data$id=rep( seq(1, nrow(data)/nObsType) , each=nObsType) 
data <- data %>%filter(complete.cases(.)) 
data$Ventas <- as.numeric(data$Ventas)
```


```{r, include=FALSE}
g <- ggplot(data, aes(x =reorder(CODIGO_SCIAN, -Ventas), y = Ventas))  +
         geom_bar(stat = "identity", aes(fill = Destino)) +
         theme(axis.text.x = element_text(angle = 60, hjust=1)) +
         coord_flip() +
         xlab('Código SCIAN') 
```

```{r, fig.height = 25, fig.width=5}
g
```

Lets make a deeper analysis in on heavy industry(defined by the Ministry of Economy as industries classified from 333 to 336) which are key in Mexican domestic industry.


###Automotive
```{r, include=FALSE}
auto <- datos %>% select(CODIGO_SCIAN, ANIO, H010B, H010C) %>% filter(CODIGO_SCIAN %in% c("336"))
```
In this section we will analyse the automotive industry in Mexico. 

```{r, include=FALSE}
#For easy handing we must use the tidy data paradigm
auto_tidy <- auto %>% gather(Genero,Numero,H010B:H010C) 
auto_tidy$Genero[auto_tidy$Genero == "H010B"] <- "Hombres"
auto_tidy$Genero[auto_tidy$Genero == "H010C"] <- "Mujeres"
```


```{r,include=FALSE}
auto1 <-  ggplot(data = auto_tidy, aes(x=ANIO, y=Numero, color=Genero)) + 
  geom_line(size=5) +
  xlab('Año') +
  ylab('Número de Empleados') +
  ggtitle("Empleados divididos por género en la industria automotriz") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
  
```


```{r}
auto1 
```

```{r, include=FALSE}
auto_ins <- datos %>% select(CODIGO_SCIAN, ANIO, K316B, K316C) %>% filter(CODIGO_SCIAN %in% c("336"))
```

```{r, include=FALSE}
#For easy handing we must use the tidy data paradigm
auto_tidy <- auto_ins %>% gather(Origen, Cantidad, K316B:K316C) 
auto_tidy$Origen[auto_tidy$Origen == "K316B"] <- "Nacional"
auto_tidy$Origen[auto_tidy$Origen == "K316C"] <- "Importado"
```

```{r,include=FALSE}
auto2 <-  ggplot(data = auto_tidy, aes(x=ANIO, y=Cantidad, color=Origen)) + 
  geom_line(size=5) +
  xlab('Año') +
  ylab('Compra de materias primas') +
  ggtitle("Volumen de Materias Primas en la industria automotriz") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_y_continuous(labels = comma)
  
```

```{r}
auto2 
```

```{r, include=FALSE}
auto_vtas <- datos %>% select(CODIGO_SCIAN, ANIO, M310B, M310C) %>% filter(CODIGO_SCIAN %in% c("336"))
```

```{r, include=FALSE}
#For easy handing we must use the tidy data paradigm
auto_tidy <- auto_vtas %>% gather(Destino, Ventas, M310B:M310C) 
auto_tidy$Destino[auto_tidy$Destino == "M310B"] <- "Nacional"
auto_tidy$Destino[auto_tidy$Destino == "M310C"] <- "Exportación"
```

```{r,include=FALSE}
auto3 <-  ggplot(data = auto_tidy, aes(x=ANIO, y=Ventas, color=Destino)) + 
  geom_line(size=5) +
  xlab('Año') +
  ylab('Venta de productos finales') +
  ggtitle("Destino de productos finales en la industria automotriz") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_y_continuous(labels = comma)
  
```

```{r}
auto3 
```

###Electrical Equipment(including household appliances)
```{r, include=FALSE}
electrical <- datos %>% select(CODIGO_SCIAN, ANIO, H010B, H010C) %>% filter(CODIGO_SCIAN %in% c( "335"))
```
In this section we will analyse the electrical manufacturing industry in Mexico. 

```{r, include=FALSE}
#For easy handing we must use the tidy data paradigm
electrical_tidy <- electrical %>% gather(Genero,Numero,H010B:H010C) 
electrical_tidy$Genero[electrical_tidy$Genero == "H010B"] <- "Hombres"
electrical_tidy$Genero[electrical_tidy$Genero == "H010C"] <- "Mujeres"
```

```{r,include=FALSE}
electrical1 <-  ggplot(data = electrical_tidy, aes(x=ANIO, y=Numero, color=Genero)) + 
  geom_line(size=5) +
  xlab('Año') +
  ylab('Número de Empleados') +
  ggtitle("Empleados divididos por género en la industria de manufacturas eléctricas") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
  
```


```{r}
electrical1 
```

```{r, include=FALSE}
electrical_ins <- datos %>% select(CODIGO_SCIAN, ANIO, K316B, K316C) %>% filter(CODIGO_SCIAN %in% c("335"))
```

```{r, include=FALSE}
#For easy handing we must use the tidy data paradigm
electrical_tidy <- electrical_ins %>% gather(Origen, Cantidad, K316B:K316C) 
electrical_tidy$Origen[electrical_tidy$Origen == "K316B"] <- "Nacional"
electrical_tidy$Origen[electrical_tidy$Origen == "K316C"] <- "Importado"
```

```{r,include=FALSE}
electrical2 <-  ggplot(data = electrical_tidy, aes(x=ANIO, y=Cantidad, color=Origen)) + 
  geom_line(size=5) +
  xlab('Año') +
  ylab('Compra de materias primas') +
  ggtitle("Volumen de Materias Primas en la industria de manufacturas eléctricas") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_y_continuous(labels = comma)
  
```

```{r}
electrical2 
```

```{r, include=FALSE}
electrical_vtas <- datos %>% select(CODIGO_SCIAN, ANIO, M310B, M310C) %>% filter(CODIGO_SCIAN %in% c("335"))
```

```{r, include=FALSE}
#For easy handing we must use the tidy data paradigm
electrical_tidy <- electrical_vtas %>% gather(Destino, Ventas, M310B:M310C) 
electrical_tidy$Destino[electrical_tidy$Destino == "M310B"] <- "Nacional"
electrical_tidy$Destino[electrical_tidy$Destino == "M310C"] <- "Exportación"
```

```{r,include=FALSE}
electrical3 <-  ggplot(data = electrical_tidy, aes(x=ANIO, y=Ventas, color=Destino)) + 
  geom_line(size=5) +
  xlab('Año') +
  ylab('Venta de productos finales') +
  ggtitle("Destino de productos finales en la industria de manufacturas eléctricas") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_y_continuous(labels = comma)
  
```

```{r}
electrical3 
```

Despite its high international competitiveness this industry heavily relies on domestic market sales.


###Electronics
```{r, include=FALSE}
electronics <- datos %>% select(CODIGO_SCIAN, ANIO, H010B, H010C) %>% filter(CODIGO_SCIAN %in% c("334"))
```
In this section we will analyse the electronics manufacturing industry in Mexico.

```{r, include=FALSE}
#For easy handing we must use the tidy data paradigm
electronics_tidy <- electronics %>% gather(Genero,Numero,H010B:H010C) 
electronics_tidy$Genero[electronics_tidy$Genero == "H010B"] <- "Hombres"
electronics_tidy$Genero[electronics_tidy$Genero == "H010C"] <- "Mujeres"
```


```{r,include=FALSE}
electronics1 <-  ggplot(data = electronics_tidy, aes(x=ANIO, y=Numero, color=Genero)) + 
  geom_line(size=5) +
  xlab('Año') +
  ylab('Número de Empleados') +
  ggtitle("Empleados divididos por género en la industria electrónica") 
  theme(plot.title = element_text(hjust = 0.5)) 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
  
```


```{r}
electronics1 
```

Not surprinsingly consisten with many studies, women dominate the electronics labor market due to its quality during the manufacturing process.

```{r, include=FALSE}
electronics_ins <- datos %>% select(CODIGO_SCIAN, ANIO, K316B, K316C) %>% filter(CODIGO_SCIAN %in% c("334"))
```

```{r, include=FALSE}
#For easy handing we must use the tidy data paradigm
electronics_tidy <- electronics_ins %>% gather(Origen, Cantidad, K316B:K316C) 
electronics_tidy$Origen[electronics_tidy$Origen == "K316B"] <- "Nacional"
electronics_tidy$Origen[electronics_tidy$Origen == "K316C"] <- "Importado"
```

```{r,include=FALSE}
electronics2 <-  ggplot(data = electronics_tidy, aes(x=ANIO, y=Cantidad, color=Origen)) + 
  geom_line(size=5) +
  xlab('Año') +
  ylab('Compra de materias primas') +
  ggtitle("Volumen de Materias Primas en la industria electrónica") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_y_continuous(labels = comma)
  
```

```{r}
electronics2 
```

```{r, include=FALSE}
electronics_vtas <- datos %>% select(CODIGO_SCIAN, ANIO, M310B, M310C) %>% filter(CODIGO_SCIAN %in% c("334"))
```

```{r, include=FALSE}
#For easy handing we must use the tidy data paradigm
electronics_tidy <- electronics_vtas %>% gather(Destino, Ventas, M310B:M310C) 
electronics_tidy$Destino[electronics_tidy$Destino == "M310B"] <- "Nacional"
electronics_tidy$Destino[electronics_tidy$Destino == "M310C"] <- "Exportación"
```

```{r,include=FALSE}
electronics3 <-  ggplot(data = electronics_tidy, aes(x=ANIO, y=Ventas, color=Destino)) + 
  geom_line(size=5) +
  xlab('Año') +
  ylab('Venta de productos finales') +
  ggtitle("Destino de productos finales en la industria electrónica") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_y_continuous(labels = comma)
  
```

```{r}
electronics3 
```

###Capital Goods
```{r}
cg <- datos %>% select(CODIGO_SCIAN, ANIO, H010B, H010C) %>% filter(CODIGO_SCIAN %in% c("333"))
```
In this section we will analyse the capital goods manufacturing industry in Mexico.

```{r, include=FALSE}
#For easy handing we must use the tidy data paradigm
cg_tidy <- cg %>% gather(Genero,Numero,H010B:H010C) 
cg_tidy$Genero[cg_tidy$Genero == "H010B"] <- "Hombres"
cg_tidy$Genero[cg_tidy$Genero == "H010C"] <- "Mujeres"
```


```{r,include=FALSE}
cg1 <-  ggplot(data = cg_tidy, aes(x=ANIO, y=Numero, color=Genero)) + 
  geom_line(size=5) +
  xlab('Año') +
  ylab('Número de Empleados') +
  ggtitle("Empleados divididos por género en la industria de bienes de capital") 
  theme(plot.title = element_text(hjust = 0.5)) 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
  
```


```{r}
cg1 
```

```{r, include=FALSE}
cg_ins <- datos %>% select(CODIGO_SCIAN, ANIO, K316B, K316C) %>% filter(CODIGO_SCIAN %in% c("333"))
```

```{r, include=FALSE}
#For easy handing we must use the tidy data paradigm
cg_tidy <- cg_ins %>% gather(Origen, Cantidad, K316B:K316C) 
cg_tidy$Origen[cg_tidy$Origen == "K316B"] <- "Nacional"
cg_tidy$Origen[cg_tidy$Origen == "K316C"] <- "Importado"
```

```{r,include=FALSE}
cg2 <-  ggplot(data = cg_tidy, aes(x=ANIO, y=Cantidad, color=Origen)) + 
  geom_line(size=5) +
  xlab('Año') +
  ylab('Compra de materias primas') +
  ggtitle("Volumen de Materias Primas en la industria de bienes de capital") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_y_continuous(labels = comma)
  
```

```{r}
cg2 
```

```{r, include=FALSE}
cg_vtas <- datos %>% select(CODIGO_SCIAN, ANIO, M310B, M310C) %>% filter(CODIGO_SCIAN %in% c("333"))
```

```{r, include=FALSE}
#For easy handing we must use the tidy data paradigm
cg_tidy <- cg_vtas %>% gather(Destino, Ventas, M310B:M310C) 
cg_tidy$Destino[cg_tidy$Destino == "M310B"] <- "Nacional"
cg_tidy$Destino[cg_tidy$Destino == "M310C"] <- "Exportación"
```

```{r,include=FALSE}
cg3 <-  ggplot(data = cg_tidy, aes(x=ANIO, y=Ventas, color=Destino)) + 
  geom_line(size=5) +
  xlab('Año') +
  ylab('Venta de productos finales') +
  ggtitle("Destino de productos finales en la industria de bienes de capital") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_y_continuous(labels = comma)
  
```

```{r}
cg3 
```

###Geographical information

We also downloaded the exports by state published by INEGI (https://www.inegi.org.mx/app/descarga/?t=0030002000000000&ag=00) to identify the geographical pattern in our country.


```{r}

```



###Findings

1.- Mexican heavy industry (333-336) heavily relies on imports for manufacturing. This suggests that despite a successful "maquiladora" program, efforts must conitnue to foster local suppliers.

2.- Most employees are male, however electronics industry relies on female employees. 

3.- Mexican heavy industry is focused on serving international markets mainly the US.

4.- Total indsutry has a different pattern. It relies on domestic markets for supplying. The biggest share of sales are in the domestic market and most employees are men.


